Toggle Smell Detection in Google Chrome

### 2015-12-08 paper/paper.tex
Fix something in the result
Add the TODO in the introduction paragraph

\documentclass[conference]{IEEEtran}
%\usepackage[top=1.2in, bottom=1.5in, left=0.8in, right=0.8in]{geometry}
\usepackage{balance}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{float}

@@

\begin{abstract}
Identifying code smell is the first step to re-factor a software system. 
In Google Chrome developers use feature toggles to control their features 
and keep developing on a single trunk. This paper investigates code smell 
caused by improper use of feature toggles in Google Chrome that we call 
as toggle smell. Using feature toggles to hide/show features is an old 
concept but recently being practised in many software companies. Improper 
use of toggles might cause code smell including duplicate code, dead code, 
coupling and lack of cohesion. We classified the smells caused by toggles 
in six different patterns Dead Toggles, Nested Toggles, Combinatorial (spaghetti) Toggles, 
Mix of Compile-Time and Runtime Toggles, Legacy toggles and Spread Toggles. 
We created a tool ``Toggle Smell Detector (TSD)'' as an Eclipse plug-in using Eclipse C++ Development Tooling (CDT) to identify these toggle 
smells in major modules of Google Chrome source code. We found TODO 
nested toggles smells, TODO spaghetti toggles and TODO spread toggles in ``chrome'' and ``base'' modules of Google Chrome.\\
\end{abstract}

@@

\section{Study Setup}
\label{study-setup}
In order to explore the feature toggle related smell we have searched for open source projects and found some projects with feature toggle implemented in those project. But we have choose Google chromium as our main code base because it has more then 5 years active development life cycle with feature toggle in it and it has rapid released. So there might be any issue with feature toggle which might not notice properly. We have used Eclipse Plugin Development Environment(PDE) which is a Java based framework, it provides support for building source code analysis applications. And we have used Eclipse C++ Development Tooling (CDT) which is Eclipse variant to support development of C/C++ applications. This is where the C++ project will be loaded from google chromium source code on the test workbench.Our toggle smell detection algorithm is implemented in java. 
\section{Case Study}
\label{results}
We classified toggle smells in different classes based on their usage in 
the source code. Before that we studied different types of feature toggles 
available in Google Chrome.

@@

\begin{table}[!h]
\caption{Dead Toggle Smell}
\centering
\begin{tabular}{|p{1.5cm}|p{6.6cm}|}
 \hline\hline
 Description & This smell is present if the toggle repository does not possess the information about the toggle flag, but the source code is still found to use the flags to encapsulate code blocks. \\ \hline
 Example & 
 \begin{lstlisting}
if(switches::toggle1){
    Do something
}else{
    Do something else
}
 \end{lstlisting}
  \\ \hline

@@

\begin{table}[!h]
\caption{TOGGLE\_STABLE}
\centering
\begin{tabular}{|p{1.5cm}|p{6.6cm}|}
 \hline\hline
 Description & This smell is observed when the feature has received enough feedback from the production environment and has been observed stable through several releases and became permanent in the product. However the code for the features are still running with the toggle check.  \\ \hline

@@

\subsection{No Dead or Stable Toggle Smell}
For our study we have taken the latest version of chromium project source code using the ``\textbf{depot\_tools}''. However for the current version we didn’t had historical data of the dead toggles. So in order to validate the dead toggle detection algorithm, we manually induced the smells in the code and verified that our algorithm is working as designed.
\\

So to confirm the behavior, we also took the earlier version of the code from the repository and ran the dead toggle smell detection algorithm and we found the following results. This prove that algorithm was indeed able to detect smells in the actual code.

>>>>

\documentclass[conference]{IEEEtran}
%\usepackage[top=1.2in, bottom=1.5in, left=0.8in, right=0.8in]{geometry}
\usepackage{balance}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{enumitem}

@@

\begin{abstract}
Identifying code smell is the first step to re-factor a software system. 
In Google Chrome developers use feature toggles to control their features 
and keep developing on a single trunk. This paper investigates code smell 
caused by improper use of feature toggles in Google Chrome that we call 
as toggle smell. Using feature toggles to hide/show features is an old 
concept but recently being practised in many software companies. Improper 
use of toggles might cause code smell including duplicate code, dead code, 
coupling and lack of cohesion. We classified the smells caused by toggles 
in six different patterns Dead Toggles, Nested Toggles, Combinatorial (spaghetti) Toggles, 
Mix of Compile-Time and Runtime Toggles, Legacy toggles and Spread Toggles. 
We created a tool ``Toggle Smell Detector (TSD)'' as an Eclipse plug-in using Eclipse C++ Development Tooling (CDT) to identify these toggle 
smells in major modules of Google Chrome source code. We found 130 
nested toggles smells, 37 spaghetti toggles and 37 spread toggles in  the following modules namely base, ui, net, media, ppapi, ash, chrome. In total we found 206 different toggle related code smells in 7 different modules from google chromium project.\\
\end{abstract}

@@

\section{Study Setup}
\label{study-setup}
In order to explore the feature toggle related smell we have searched for open source projects and found some projects with feature toggle implemented in those project. But we have choose Google chromium as our main code base because it has more then 5 years active development life cycle with feature toggle in it and it has rapid releases. We have used Eclipse Plugin Development Environment(PDE) which is a Java based framework, it provides support for building source code analysis applications. And we have used Eclipse C++ Development Tooling (CDT) which is Eclipse variant to support development of C/C++ applications. This is where the C++ project will be loaded from google chromium source code on the test workbench.Our toggle smell detection algorithm is implemented in java. 
\section{Case Study}
\label{results}
We classified toggle smells in different classes based on their usage in 
the source code. Before that we studied different types of feature toggles 
available in Google Chrome.

@@

\begin{table}[!h]
\caption{Dead Toggle Smell}
\centering
\begin{tabular}{|p{1.5cm}|p{7cm}|}
 \hline\hline
 Description & This smell is present if the toggle repository does not possess the information about the toggle flag, but the source code is still found to use the flags to encapsulate code blocks. \\ \hline
 Example & 
 \begin{lstlisting}
if(switches::toggle1){
    Do something
}else{
    Do something else
}
 \end{lstlisting}
  \\ \hline

@@

\begin{table}[ht]
\caption{TOGGLE\_STABLE}
\centering
\begin{tabular}{|p{1.5cm}|p{6.6cm}|}
 \hline\hline
 Description & This smell is observed when the feature has received enough feedback from the production environment and has been observed stable through several releases and became permanent in the product. However the code for the features are still running with the toggle check.  \\ \hline

@@

\subsection{No Dead or Stable Toggle Smell}
For our study we have taken the latest version of chromium project source code using the ``\textbf{depot\_tools}''. However for the current version we didn’t had historical data of the dead toggles. So in order to validate the dead toggle detection algorithm, we manually induced the smells in the code and verified that our algorithm is working as designed.
